\papertitle

### 2013-01-30 manuscript.tex
final commit before going home

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithopter}

@@

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
The ground station guides the H$^2$Bird by setting the
reference attitude of its on-board attitude 
controller (Figs.\ref{fig:process_flow} and~\ref{fig:block_diagram}). Using 
the estimate of 2D vehicle pose from the pose estimation algorithm, the 
ground station calculates an altitude error and horizontal error. The ground 
station then uses a PID control law to calculate a new reference attitude, 
which it sends to the H$^2$Bird over radio. 
We apply a fixed-lag window to the PID 
controller integral term to prevent wind-up while we launch the ornithopter. 
We tuned the proportional and derivative terms of this outer controller to 
dampen the overshoot and drift caused by the cooperative system latency.
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/pf_screencap.pdf}
\caption{Frame sequence from video feed used for tracking. Particles 
are shown in \textcolor{red}{red}, the current state estimate as a 
\textcolor{yellow}{yellow} circle, the window bounding box in
\textcolor{blue}{blue}, and the target location as a \textcolor{green}{green} 
circle. 1.~Particles initialized uniformly across the frame; 2.~Human operator 
dragging bounding box across the window; 3.~H$^2$Bird enters the frame. 
Particles converge on its location; 4.~Release H$^2$Bird, which 
begins cooperative autonomous flight toward the target; 5.~Visual servoing 
controller overshoots the window on the left, and commands a right-turn 
maneuver to recover; 6.~H$^2$Bird successfully navigates through the window.}
\label{fig:pf_screencap}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}

We develop a new flapping-winged MAV and

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithopter}

@@

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
The ground station guides the H$^2$Bird by setting the
reference attitude of its on-board attitude 
controller (Figs.\ref{fig:process_flow} and~\ref{fig:block_diagram}). Using 
the estimate of 2D vehicle pose from the pose estimation algorithm, the 
ground station calculates an altitude error and horizontal error. The ground 
station then uses a PID control law to calculate a new reference pitch and yaw, 
which it sends to the H$^2$Bird over radio. 
We apply a fixed-lag window to the PID 
controller integral term to prevent wind-up while we launch the ornithopter. 
We tuned the proportional and derivative terms of this outer controller to 
dampen the overshoot and drift caused by the cooperative system latency.
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/pf_screencap.pdf}
\caption{Frame sequence from video feed used for tracking. Particles 
are shown in \textcolor{red}{red}, the current state estimate as a 
\textcolor{yellow}{yellow} circle, the window bounding box in
\textcolor{blue}{blue}, and the target location as a \textcolor{green}{green} 
circle. 1.~Particles initialized uniformly across the frame; 2.~Human operator 
dragging bounding box across the window; 3.~H$^2$Bird enters the frame. 
Particles converge on its location; 4.~Release H$^2$Bird, which h
begins cooperative autonomous flight toward the target; 5.~Visual servoing 
controller overshoots the window on the left, and commands a right-turn 
maneuver to recover; 6.~H$^2$Bird successfully navigates through the window.}
\label{fig:pf_screencap}
\end{figure}
